### 2016-03-10 paper5.tex
Derotated some figures, and put all table captions above the table.

For each observed early-type star, we generate several synthetic binary star observations by adding model spectra for stars with $T_\mathrm{eff} = 3000 - 7000$ K in steps of 100 K and rotational velocities $v\sin{i} = 0 - 50$ $\\mathrm{km\ s}^{-1}$ in steps of 10 $\mathrm{km\ s}^{-1}$. For each temperature and $v\sin{i}$ combination, we make 17 independent synthetic observations by adding the model to the data with a radial velocity shift between -400 to 400 $\mathrm{km\ s}^{-1}$ in steps of 50 $\mathrm{km\ s}^{-1}$. We label a companion as detected if the highest peak in the CCF of the synthetic data with the model spectrum of the same temperature is within 5 $\mathrm{km\ s}^{-1}$ (the approximate instrumental broadening) of the correct velocity.

>>>>

For each observed early-type star, we generate several synthetic binary star observations by adding model spectra for stars with $T_\mathrm{eff} = 3000 - 7000$ K in steps of 100 K and rotational velocities $v\sin{i} = 0 - 50$ $\mathrm{km\ s}^{-1}$ in steps of 10 $\mathrm{km\ s}^{-1}$. For each temperature and $v\sin{i}$ combination, we make 17 independent synthetic observations by adding the model to the data with a radial velocity shift between -400 to 400 $\mathrm{km\ s}^{-1}$ in steps of 50 $\mathrm{km\ s}^{-1}$. We label a companion as detected if the highest peak in the CCF of the synthetic data with the model spectrum of the same temperature is within 5 $\mathrm{km\ s}^{-1}$ (the approximate instrumental broadening) of the correct velocity.
